Data Management for LSST Special Programs

### 2023-10-18 sec_sci.tex
fix ref

Further discussion of regular Prompt processing of Special Programs data, with
examples and a discussion of a few challenges,
is provided in Section~\ref{ssec:proc_reg_prompt}.

>>>>

Further discussion of regular Prompt processing of Special Programs data, with
examples and a discussion of a few challenges,
is provided in Section~\ref{sssec:proc_reg_prompt}.
